# Demo

- `CreateTweet()`: Create tweet using parameters.
- Parameters:
  - `author_avatar` (str): avatar of author
  - `author_name` (str): name of author
  - `author_tag` (str): twitter username/handle of author
  - `text` (str): main text of tweet
  - `reactions_retweet` (str): number of reactions of tweet
  - `reactions_quote` (str): number of quotes of tweet
  - `reactions_like` (str): number of likes of tweet
  - `time` (str/NULL/None): time of tweet in format "2022-07-05 14:34"; if None use current time
  - `quote` (TRUE/FALSE): whether or not to print quoted tweet
  - `quote_author_avatar` (str): avatar of author of quoted tweet
  - `quote_author_name` (str): name of author of quoted tweet
  - `quote_author_tag` (str): twitter username/handle of author of quoted tweet
  - `quote_text` (str): text of quoted tweet
- Returns:
  - image: Twitter image in PIL Image format

```{r}
# install.packages("reticulate")
library("reticulate")
source_python('conjoint_tweets.py')
image = CreateTweet(
    author_avatar="input/avatar/woman_clean.png",
    author_name="Daydream Whale",
    author_tag="@DaydreamWhale",
    text="Grim-visaged war hath smooth'd his wrinkled front; And now, instead of 
    mounting barded steeds. To fright the souls of fearful adversaries, He 
    capers nimbly in a lady's chamber. To the lascivious pleasing of a lute.",
    reactions_retweet="100",
    reactions_quote="200",
    reactions_like="20K",
    time=NULL,
    quote=TRUE,
    quote_author_avatar="input/avatar/woman_clean.png",
    quote_author_name="Mobsteroid",
    quote_author_tag="@mobsteroid",
    quote_text="Now is the winter of our discontent. Made glorious summer by 
    this sun of York; And all the clouds that lour'd upon our house. In the deep 
    bosom of the ocean buried. Now are our brows bound with victorious wreaths. 
    Our bruised arms hung up for monuments. Our stern alarums changed to merry 
    meetings, Our dreadful marches to delightful measures."
)
SaveTweet(image, "output/test_save_from_R.png", quality = 95)
```

```{r message=FALSE, warning = FALSE}
# install.packages("magick")
library("magick")
image_array = Convert(image)
tweet = magick::image_read(image_array)
print(tweet)
```

